Fields COVID-19 dataset exploration

### 2023-01-04 data_cleaning/Data_cleaning_and_covariates_Jan_03.qmd
Clean dataset created

write.csv(test,here("data","missing_municipalities.csv"),row.names = FALSE)

@@

```{r,merge-datasets-2}

>>>>

#write.csv(test,here("data","missing_municipalities.csv"),row.names = FALSE)

@@

```{r,merge-datasets-2}
#load missing municipalities dataset

missing_municipalities<-read.csv(here("data","missing_municipalities_updated.csv"))

#combining geographical regions

clean_data<-clean_data %>%
  left_join(missing_municipalities, by = c("city")) %>%
  mutate(Geographic.area = coalesce(Geographic.area.x,Geographic.area.y)) %>%
  select(-c(Geographic.area.x,Geographic.area.y))

clean_data$Geographic.area<-as.factor(clean_data$Geographic.area)

# load the the titles for each region

geographic_areas<-read.csv(here("data","geographic_areas.csv"))

geographic_areas$Geographic.area<-as.factor(geographic_areas$Geographic.area)

geographic_areas$Geographic.area.title <-as.factor(geographic_areas$Geographic.area.title)

#merge the datasets

clean_data <-left_join(clean_data,geographic_areas,by="Geographic.area")
